%-------------------------
% Resume in LaTeX
% Author : Adapted for Sukanya
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeHeading}[4]{
	\begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\Large Sukanya} & Email: \href{mailto:sukanya104146@gmail.com}{sukanya104146@gmail.com}\\
		\href{https://www.linkedin.com/in/sukanya-7b8118168/}{linkedin.com/in/sukanya-7b8118168} & Mobile: +91-9006536109 \\
	\end{tabular*}
	
	%-----------SUMMARY-----------------
	\section{Professional Summary}
	Front-End Developer with 6 years of experience delivering responsive web and mobile applications across finance, e-commerce, and networking domains. Proficient in React.js, React Native, TypeScript, Redux, and Next.js. Skilled in writing unit and integration tests, enhancing accessibility, and collaborating within Agile teams to deliver high-quality products.
	
		%-----------EDUCATION-----------------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{Birla Institute of Technology, Mesra}{Ranchi, India}
	{Bachelor of Engineering}{2015 -- 2019}
	\resumeSubHeadingListEnd
	
%-----------TECHNICAL SKILLS-----------------
\section{Technical Skills}
\begin{tabularx}{\textwidth}{X @{\hspace{1cm}} X}
	\textbf{Languages/Frameworks:} HTML5, CSS3, JavaScript, TypeScript, React.js, React Native, Next.js, Redux, Redux Saga
	&
	\textbf{Testing:} Jest, Cypress
	\\[4pt]
	\textbf{Version Control:} Git, GitHub, GitLab
	&
	\textbf{Database:} MySQL
	\\[4pt]
	\textbf{Tools:} Visual Studio Code, Xcode, JIRA
	&
	\textbf{OS:} Windows, macOS
\end{tabularx}
	
	%-----------EXPERIENCE-----------------
	\section{Experience}
	\resumeSubHeadingListStart
	
	\resumeSubheading
	{Accenture}{India}
	{Custom Software Engineering Analyst}{April 2023 -- Present}
	\resumeItemListStart
	\resumeItem{}
	{Developed core features for the retail web app, including the \textbf{shopping cart}, listing, and confirmation pages.}
	\resumeItem{}
	{Built responsive UI components with \textbf{Next.js}, \textbf{TypeScript}, \textbf{Redux}, and \textbf{Redux Saga}.}
	\resumeItem{}
	{Created unit tests in \textbf{Jest} to support high-quality releases and reduce regressions.}
	\resumeItemListEnd
	
	\resumeSubheading
	{Accenture}{India}
	{Custom Software Engineering Analyst}{March 2023 -- Present}
	\resumeItemListStart
	\resumeItem{}
	{Developed \textbf{cart} and \textbf{promo code} workflows for a financial web app using \textbf{Next.js}, \textbf{TypeScript}, and \textbf{Redux}.}
	\resumeItem{}
	{Built accessible, responsive UI components aligned with \textbf{web standards}.}
	\resumeItem{}
	{Created unit and integration tests with \textbf{Jest} and \textbf{Cypress} to ensure stability.}
	\resumeItemListEnd
	
	\resumeSubheading
	{Accenture}{India}
	{Custom Software Engineering Analyst}{July 2021 -- February 2023}
	\resumeItemListStart
	\resumeItem{}
	{Led the development of critical e-commerce features for an iOS React Native app, including product listing, shopping cart, order details, and confirmation flows for vehicle accessories and on-demand services.}
	\resumeItem{}
	{Implemented robust state management using Redux and Redux Saga, ensuring consistent, real-time updates across cart operations, order processing, and service scheduling.}
	\resumeItem{}
	{Integrated REST APIs to enable dynamic content retrieval and secure transaction workflows, supporting complex scenarios such as scheduling home or garage services.}
	\resumeItem{}
	{Maintained 85\% unit test coverage with Jest and participated in Agile ceremonies, contributing to predictable delivery cycles and high-quality feature releases.}
	\resumeItemListEnd
	
	
	\resumeSubheading
	{Cognizant Technology Solutions}{India}
	{Software Engineer}{July 2019 -- July 2021}
	\resumeItemListStart
	\resumeItem{}
	{Built a \textbf{fund transfer web application} enabling customers to access and track transfer requests for a \textbf{retirement plan recordkeeping financial holding company}.}
	\resumeItem{}
	{Implemented \textbf{web accessibility features} to improve the experience for users with visual and motor impairments.}
	\resumeItem{}
	{Developed scalable, consistent state management using \textbf{React.js}, \textbf{Redux}, and \textbf{TypeScript}.}
	\resumeItem{}
	{Achieved \textbf{80\% test coverage} with \textbf{Jest} to ensure stability and reliability.}
	\resumeItem{}
	{Collaborated in Agile teams to deliver features incrementally and meet project milestones.}
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	

	
\end{document}