%-------------------------
% Resume in LaTeX
% Author : Adapted for Sukanya
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{ #2. \vspace{-2pt}}
	}
}

\newcommand{\resumeHeading}[4]{
	\begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\href{http://sourabhbajaj.com/}{\Large Sukanya}} & Email : \href{mailto:sukanya104146@gmail.com}{sukanya104146@gmail.com}\\
		\href{https://www.linkedin.com/in/sukanya-7b8118168/}{linkedin.com/in/sukanya-7b8118168} & Mobile : +91-9006536109 \\
	\end{tabular*}
	
	%-----------SUMMARY-----------------
	\section{Professional Summary}
	Front-End Developer with 6 years of experience building responsive web and mobile applications in finance, e-commerce, and networking. Proficient in React.js, React Native, TypeScript, Redux, and Next.js. Skilled in testing, accessibility, and Agile collaboration to deliver high-quality products.
	
	%-----------EDUCATION-----------------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{Birla Institute of Technology, Mesra}{Ranchi, India}
	{Bachelor of Engineering}{2015 -- 2019}
	\resumeSubHeadingListEnd
	
%-----------TECHNICAL SKILLS-----------------
\section{Technical Skills}

\textbf{Languages:} HTML, CSS, JavaScript, TypeScript \\
\textbf{Frameworks:} React.js, React Native, Next.js, Redux, Redux Saga, Tailwind CSS \\
\textbf{Testing:} Jest, Cypress \\
\textbf{Version Control:} Git, GitHub, GitLab, SourceTree \\
\textbf{Tools:} Visual Studio Code, Xcode, JIRA \\
\textbf{Operating Systems:} Windows, macOS, Linux
	
	%-----------EXPERIENCE-----------------
	\section{Experience}
	\resumeSubHeadingListStart
	
\resumeSubheading
{Accenture}{India}
{Custom Software Engineering Analyst}{January 2025 -- Present}
\resumeItemListStart
\resumeItem{\textbf{Project Details:}}{E-commerce web application for a multinational mass media, telecommunications, and entertainment company.}
\resumeItem{}{Designed and developed core retail web app features, including the shopping cart, listings, and confirmation pages}
\resumeItem{}{Built scalable, reusable, and accessible UI components using Next.js, TypeScript, Redux, and Redux Saga, improving development efficiency and consistency}
\resumeItem{}{Enhanced application performance and responsiveness through code-splitting and efficient state management}
\resumeItem{}{Implemented robust unit and integration testing with Jest and Cypress, increasing release confidence and reducing regression defects}
\resumeItemListEnd
	
\resumeSubheading
{Accenture}{India}
{Custom Software Engineering Analyst}{March 2023 -- December 2024}
\resumeItemListStart
\resumeItem{\textbf{Project Details:}}{End-to-End Financial Workflow Web Interface for a global financial investment management and insurance company.}
\resumeItem{}{Enhanced key financial web app modules (Dashboard, Setup, Contributions, Loans, Review \& Submit, Confirmation) by improving UI, functionality, and accessibility.}
\resumeItem{}{Developed responsive and accessible UI components aligned with WCAG standards using Next.js, TypeScript, and Redux.}
\resumeItem{}{Ensured application stability through comprehensive unit and integration testing with Jest and Cypress, and proactively resolved production issues.}
\resumeItem{}{Collaborated in Agile teams to deliver user-centric features and mentored new team members to support critical releases.}
\resumeItemListEnd
	
\resumeSubheading
{Accenture}{India}
{Custom Software Engineering Analyst}{July 2021 -- February 2023}
\resumeItemListStart
\resumeItem{\textbf{Project Details:}}{iOS Application for a major US Car Accessories Retailer.}
\resumeItem{}{Designed and developed key e-commerce features for an iOS React Native app, including product selection, cart, order details, payment, and confirmation flows for vehicle accessories.}
\resumeItem{}{Improved the mobile web experience for associates by building responsive, user-friendly UI components and developed an iPad-specific version of the application.}
\resumeItem{}{Implemented efficient and scalable state management using Redux and Redux Saga for consistent cart operations, order processing, and scheduling.}
\resumeItem{}{Actively contributed to Agile processes, resolved critical bugs to improve app stability, and maintained 85\% unit test coverage with Jest to ensure defect-free releases.}
\resumeItemListEnd
	
\resumeSubheading
{Cognizant Technology Solutions}{India}
{Senior System Engineer}{July 2019 -- July 2021}
\resumeItemListStart
\resumeItem{\textbf{Project Details:}}{Retirement Plan Fund Transfer Tracking Web Application for a leading US financial holding company.}
\resumeItem{}{Developed a fund transfer web application that enabled customers to access and track their transfer requests.}
\resumeItem{}{Implemented web accessibility features to enhance the experience for users with disabilities.}
\resumeItem{}{Designed scalable and consistent state management using React.js, Redux, and TypeScript.}
\resumeItem{}{Achieved 80\% test coverage with Jest to ensure application stability and reliability.}
\resumeItem{}{Collaborated within an Agile framework to deliver features incrementally and meet project milestones.}
\resumeItemListEnd
	
	\resumeSubheading
	{Cognizant Technology Solutions}{India}
	{Software Engineer Intern}{Jan 2019 -- Mar 2019}
	\resumeItemListStart
	\resumeItem{}{Developed an e-learning platform for course purchase and upload using React.js and Redux}
	\resumeItem{}{Created responsive UI components aligned with project specifications}
	\resumeItem{}{Implemented unit tests in Jest to validate key features}
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
\end{document}